Functional Pearl \\ Programming with Negative, Fractional, and Imaginary Types

### 2012-02-20 dual.tex
imaginary

Imaginary types have also appeared in the literature: we relegate the
connections to Sec.~\ref{related} and proceed with a simple explanation. We
have so far extended the set of types to be the rational numbers. Now we will
push this and extend the set of types to algebraic numbers. In other words,
we will allow datatypes defined by arbitrary polynomials and allow the roots
of such polynomials to be types. Consider the type of binary trees:
\begin{verbatim}
data B = 1 + B * B
\end{verbatim}
Rearranging the terms, this declaration introduces the polynomial $b^2 - b +
1 = 0$ whose roots are $(1 \pm i\sqrt{3}) / 2$.

>>>>

Imaginary types have also appeared in the literature: we relegate the
connections to Sec.~\ref{related} and proceed with a simple explanation. We
have so far extended the set of types to be the rational numbers. Now we will
push this and extend the set of types to algebraic numbers. In other words,
we will allow datatypes defined by arbitrary polynomials and allow the roots
of such polynomials to be types. Consider the type of binary trees:
\begin{verbatim}
data B = 1 + B * B
\end{verbatim}
In conventional settings, this declaration introduces an isomorphism between
$b$ and $1+b^2$ (whose two sides are commonly known as {{fold}} and
{{unfold}}). In our setting, this induces an isomorphism between $0$ and $b^2
- b + 1$. The latter polynomial has roots $(1 \pm i\sqrt{3}) / 2$ and hence
we have two isomorphisms between $b - (1 + i\sqrt{3})$ and $0$ and also
between $b - (1 - i\sqrt{3})$ and $0$.

Now say I want to produce a value of type $b$. We can use the isomorphisms
above to break this task in many ways. Essentially exploit that $b$ is
isomorphic to $b^7$, let the various program components produce the various
parts of $b^7$ and merge them.
